Effectiveness of visual test in linear regression diagnositics

### 2022-07-29 paper_comparison/paper_comparison/paper_comparison.Rmd
update power analysis

if (!file.exists(here::here("data/third_study/conv_result.rds"))) {
  conv_result <- list()
  for (i in 1:100) {
    conv_result[[i]] <- map(1:100000,
                            function(x) {
                     shape <- sample(1:4, 1)
                     e_sigma <- sample(c(0.5, 1, 2, 4), 1)
                     x_dist <- sample(c("uniform", "normal", "lognormal", "even_discrete"), 1)
                     x <- switch(x_dist,
                                 uniform = rand_uniform(-1, 1),
                                 normal = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))},
                                 lognormal = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))},
                                 even_discrete = rand_uniform_d(k = 5, even = TRUE))
                     mod <- poly_model(shape, x = x, sigma = e_sigma)
                     n <- sample(c(50, 100, 300), 1)
                     tmp_dat <- mod$gen(n)

                     tibble(shape = shape,
                            e_sigma = e_sigma,
                            x_dist = x_dist,
                            n = n,
                            effect_size = mod$effect_size(tmp_dat),
                            p_value = mod$test(tmp_dat)$p_value,
                            reject = p_value < 0.05)
                   }) %>%
  reduce(bind_rows) %>%
  mutate(reject = as.numeric(reject))
  }

@@

@@

>>>>

if (!file.exists(here::here("data/third_study/conv_result.rds"))) {
  conv_result <- list()
  for (i in 1:100)
  {
    conv_result[[i]] <- map(1:2000,
                            function(x) {
                     shape <- sample(1:4, 1)
                     e_sigma <- sample(c(0.5, 1, 2, 4), 1)
                     x_dist <- sample(c("uniform", "normal", "lognormal", "even_discrete"), 1)
                     x <- switch(x_dist,
                                 uniform = rand_uniform(-1, 1),
                                 normal = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))},
                                 lognormal = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))},
                                 even_discrete = rand_uniform_d(k = 5, even = TRUE))
                     mod <- poly_model(shape, x = x, sigma = e_sigma)
                     n <- sample(c(50, 100, 300), 1)
                     tmp_dat <- mod$gen(n)

                     tibble(shape = shape,
                            e_sigma = e_sigma,
                            x_dist = x_dist,
                            n = n,
                            effect_size = mod$effect_size(tmp_dat),
                            p_value = mod$test(tmp_dat)$p_value,
                            reject = p_value < 0.05,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows) %>%
  mutate(reject = as.numeric(reject))
  }

  conv_result <- conv_result %>%
    reduce(bind_rows)

@@

```{r}
if (!file.exists(here::here("data/third_study/wrong_BP_conv_result.rds"))) {
  wrong_BP_conv_result <- list()
  for (i in 1:100)
  {
    wrong_BP_conv_result[[i]] <- map(1:2000,
                            function(x) {
                     shape <- sample(1:4, 1)
                     e_sigma <- sample(c(0.5, 1, 2, 4), 1)
                     x_dist <- sample(c("uniform", "normal", "lognormal", "even_discrete"), 1)
                     x <- switch(x_dist,
                                 uniform = rand_uniform(-1, 1),
                                 normal = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))},
                                 lognormal = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))},
                                 even_discrete = rand_uniform_d(k = 5, even = TRUE))
                     mod <- poly_model(shape, x = x, sigma = e_sigma)
                     n <- sample(c(50, 100, 300), 1)
                     tmp_dat <- mod$gen(n)

                     tibble(shape = shape,
                            e_sigma = e_sigma,
                            x_dist = x_dist,
                            n = n,
                            effect_size = mod$effect_size(tmp_dat),
                            p_value = HETER_MODEL$test(tmp_dat)$p_value,
                            reject = p_value < 0.05,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows) %>%
  mutate(reject = as.numeric(reject))
  }

  wrong_BP_conv_result <- wrong_BP_conv_result %>%
    reduce(bind_rows)

  saveRDS(wrong_BP_conv_result, here::here("data/third_study/wrong_BP_conv_result.rds"))
} else {
  wrong_BP_conv_result <- readRDS(here::here("data/third_study/wrong_BP_conv_result.rds"))
}

```{r}
if (!file.exists(here::here("data/third_study/wrong_WS_conv_result.rds"))) {
  wrong_WS_conv_result <- list()
  for (i in 1:100)
  {
    wrong_WS_conv_result[[i]] <- map(1:2000,
                            function(x) {
                     shape <- sample(1:4, 1)
                     e_sigma <- sample(c(0.5, 1, 2, 4), 1)
                     x_dist <- sample(c("uniform", "normal", "lognormal", "even_discrete"), 1)
                     x <- switch(x_dist,
                                 uniform = rand_uniform(-1, 1),
                                 normal = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))},
                                 lognormal = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))},
                                 even_discrete = rand_uniform_d(k = 5, even = TRUE))
                     mod <- poly_model(shape, x = x, sigma = e_sigma)
                     n <- sample(c(50, 100, 300), 1)
                     tmp_dat <- mod$gen(n)

                     tibble(shape = shape,
                            e_sigma = e_sigma,
                            x_dist = x_dist,
                            n = n,
                            effect_size = mod$effect_size(tmp_dat),
                            p_value = shapiro.test(tmp_dat$.resid)$p.value,
                            reject = p_value < 0.05,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows) %>%
  mutate(reject = as.numeric(reject))
  }

  wrong_WS_conv_result <- wrong_WS_conv_result %>%
    reduce(bind_rows)

  saveRDS(wrong_WS_conv_result, here::here("data/third_study/wrong_WS_conv_result.rds"))
} else {
  wrong_WS_conv_result <- readRDS(here::here("data/third_study/wrong_WS_conv_result.rds"))
}

@@

```{r}
conv_test_plot <- function() {
  conv_result %>%
  ggplot() +
  stat_smooth(geom = "line", 
              aes(log(effect_size), reject, group = boot_id, col = "F-test"), 
              se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 0.05) +
  stat_smooth(geom = "line", 
              aes(log(effect_size), reject, col = "F-test"), 
              se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 1) +
  labs(col = "Test") +
  theme_light() +
  xlab(quote(log[e](E))) +
  ylab("Power")
}

conv_test_plot()
```

```{r}
add_wrong_BP_conv_test_plot_layers <- function(p) {
  p +
  stat_smooth(data = wrong_BP_conv_result, geom = "line", 
              aes(log(effect_size), reject, group = boot_id, col = "BP-test"), 
              se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 0.05) +
  stat_smooth(data = wrong_BP_conv_result, geom = "line", 
              aes(log(effect_size), reject, col = "BP-test"), 
              se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 1)
}

conv_test_plot() %>%
  add_wrong_BP_conv_test_plot_layers()
```

```{r}
add_wrong_WS_conv_test_plot_layers <- function(p) {
  p +
  stat_smooth(data = wrong_WS_conv_result, geom = "line", 
              aes(log(effect_size), reject, group = boot_id, col = "WS-test"), 
              se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 0.05) +
  stat_smooth(data = wrong_WS_conv_result, geom = "line", 
              aes(log(effect_size), reject, col = "WS-test"), 
              se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 1)
}

conv_test_plot() %>%
  add_wrong_BP_conv_test_plot_layers() %>%
  add_wrong_WS_conv_test_plot_layers()
```

```{r}
boot_dat <- function(dat, times = 100) {
  result <- mutate(dat, boot_id = 1)
  for (i in 2:times) {
    result <- bind_rows(result, mutate(dat[sample(1:nrow(dat), replace = TRUE), ], boot_id = i)) 
  }
  result
}

add_visual_test_plot_layers <- function(p) {
  visual_dat <- polynomials %>%
  group_by(lineup_id) %>%
  summarise(across(c(type:p_value), first)) %>%
  filter(lineup_id < 577) %>%
  mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>%
  boot_dat(times = 100)

  p +
  stat_smooth(data = filter(visual_dat, boot_id == 1), geom = "line", 
              aes(log(effect_size), reject, group = boot_id, col = "Visual"), 
              method = "glm", method.args = list(family = binomial), se = FALSE, alpha = 1) +
  stat_smooth(data = visual_dat, geom = "line", 
              aes(log(effect_size), reject, group = boot_id, col = "Visual"), 
              method = "glm", method.args = list(family = binomial), se = FALSE, alpha = 0.05)

}

control_col <- function(p, ...) {
  p + scale_color_manual(values = unlist(list(...)))
}

conv_test_plot() %>%
  add_wrong_BP_conv_test_plot_layers() %>%
  add_wrong_WS_conv_test_plot_layers() %>%
  add_visual_test_plot_layers()
```

```{r}
polynomials %>%
  group_by(lineup_id) %>%
  summarise(across(c(type:p_value), first)) %>%
  filter(lineup_id < 577) %>%
  mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>%
  ggplot() +
  geom_smooth(aes(log(effect_size), reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_smooth(data = conv_result, aes(log(effect_size), reject, col = "Conventional test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  xlab("Natural logarithm of effect size") +
  ylab("Power")
```

### 2022-07-29 paper_comparison/paper_comparison/paper_comparison.tex
update power analysis

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-4-1.pdf}

>>>>

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-6-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-7-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-8-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-9-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-10-1.pdf}

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-11-1.pdf}
